Uncertainty Quantification in Multiscale Models of Charge Transport in Organic Semiconductors: Influence of the Exhange-Correlation Functional

### 2025-05-15 submit/paper.tex
started on a revision

\begin{figure*}[tbp]
  \centering
  \includegraphics[width=\linewidth]{figs/MSM2.pdf}
  \caption{Schematic representation of the multiscale framework for simulation of charge transport: (a) a representative large-scale morphology is obtained from Molecular Dynamics. (b) Information about the molecular building blocks and the morphology are used to determine the molecular transport graph $\mathbf{G}$ for a given choice of the \ahfx via calculation of reorganization energy, site energies, and electronic couplings. (c) The time-of-flight charge mobility is simulated based on the graph.}
  \label{fig:MSM}
\end{figure*}

@@

\begin{figure}[tbp]
    \centering
    \includegraphics[width=\linewidth]{figs/fig_autogen.pdf}
    \caption{Dependence of molecular parameters as used directly in the multiscale model or in its paramaterization phase on the amount of Hartree--Fock type exchange in the PBE0-based hybrid functional $\alpha_\text{HFX}$. (a) The adiabatic ionization potential, (b) reorganization energy, (c) dipole moment of the neutral molecule, and (d) isotropic molecular polarizability in neutral and charged states, respectively.}
    \label{fig:autogen_MADN}
\end{figure}

@@

\begin{figure*}[tbp]
  \centering
  \includegraphics[width=\linewidth]{figs/scatterE_qmmm.pdf}
  \caption{Panels (a)-(e): Scatter plot of site energies of the MADN system for different values of \ahfx vs the PBE0 ($\ahfx=0.25$) reference. (f) Site energy disorder $\sigma$ in \unit[]{eV} for all values of \ahfx.}
  \label{fig:E_qmmm_MADN}
\end{figure*}

@@

\begin{figure*}[tbp]
  \centering
  \includegraphics[width=\linewidth]{figs/scatterJ_all.pdf}
  \caption{Scatter plot of electronic coupling elements of the MADN system for different values of \ahfx vs the PBE0 ($\ahfx=0.25$) reference.}
  \label{fig:J_MADN}
\end{figure*}

@@

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\linewidth]{figs/fig_network_all.pdf}
  \caption{The maximum size of the subgraphs obtained in the percolation algorithm as a function of critical value $J_c$.}
  \label{fig:J_percolate}
\end{figure}

@@

\begin{figure}[tbp]
  \centering
  \includegraphics[width=0.45\textwidth]{figs/fig_mle_MADN_withE.pdf}
  \caption{Distribution of ToFs in the MADN system from  Monte Carlo sampling with a sample size $N_\text{MC}=50000$. The red vertical lines indicate the lower bound and upper bound of the 99\% confidence interval around the median. The black circles indicate the ToF obtained using explicit \ahfx values. Uncertainties considered are (a) in the eorganziation energy, (b) in the site energy, (c) in the coupling elements, and (d) in all simultaneously.}
  \label{fig:mle_MADN_withE}
\end{figure}

@@

\begin{figure}[tbp]
    \centering
    \includegraphics[width=\linewidth]{figs/fig_mle_withE_mu2_ave.pdf}
    \caption{Distribution of the mobility $\mu$ for different values of the externally applied electric field $F$ as obtained from uncertainty quantification using 
    Monte Carlo sampling with a sample size $N_\text{MC}=10000$. The red vertical lines indicate the lower bound and upper bound of the 99\% confidence interval around the median. (a) $|\vec{F}|=4 \cdot 10^7 \unit{V/m}$, (b) $|\vec{F}|=5 \cdot 10^7 \unit{V/m}$, (c) $|\vec{F}|=6 \cdot 10^7 \unit{V/m}$, (d) $|\vec{F}|=7 \cdot 10^7 \unit{V/m}$, (e) $|\vec{F}|=8 \cdot 10^7 \unit{V/m}$, (f) $|\vec{F}|=9 \cdot 10^7 \unit{V/m}$.}
    \label{fig:fig_mle_withE_mu2_ave}
\end{figure}

@@

\begin{figure}[tbp]
    \centering
    \includegraphics[width=0.45\textwidth]{figs/fig_PF_plot_ave.pdf}
    \caption{Electric-field dependence of the mobility $\mu$ in the multiscale modeled MADN system. The dash lines are Poole--Frenkel plots obtained with specific \ahfx values, and the green shaded area indicates the 99\% confidence interval estimated from the MC sampling with a sample size of $N_\text{MC}=10000$.}
    \label{fig:PF_plot_ave}
\end{figure}

@@

\section{Discussion \& Conclusion}
One key observation of this study of Uncertainty Quantification in multiscale models for charge transport in organic semiconductors due to the choice of exchange-correlation functionals in density functional theory by systematically varying the Hartree--Fock exchange fraction in hybrid functionals is the dominance of site energy uncertainties in influencing the variability of the time-of-flightand mobility predictions. In contrast, the uncertainties in reorganization energies and electronic coupling elements are shown to have a relatively minor effect. This suggests that further efforts to enhance the accuracy of site energy calculations -- potentially through improved parameterization or advanced quantum mechanical methods -- could significantly improve the reliability of multiscale modeling predictions.   Interestingly, the results also demonstrate that the uncertainties in electronic coupling elements, particularly those with very small magnitudes, are less relevant for overall charge transport. This aligns with the percolation analysis, which indicates that coupling elements below a critical threshold contribute minimally to the connectivity of the charge transport network. Thus, simplifying approximations in handling these low-value couplings could be justified in specific scenarios to reduce computational complexity without compromising accuracy.

@@

\bibliography{references}

\appendix*
\section{Electrostatic and polarized energy contributions}
\begin{figure*}
  \centering
  \includegraphics[width=0.80\textwidth]{figs/scatterEstat_qmmm.pdf}
  \caption{Panels (a)-(e): Scatter plot of the electrostatic contribution to site energies of the MADN system for different values of \ahfx vs the PBE0 ($\ahfx=0.25$) reference. (f) Site energy disorder $\sigma$ in \unit[]{eV} for all values of \ahfx.}
  \label{fig:Estat_qmmm_MADN}
\end{figure*}

\begin{figure*}
  \centering
  \includegraphics[width=0.80\textwidth]{figs/scatterEdip_qmmm.pdf}
  \caption{Panels (a)-(e): Scatter plot of polarization contribution to site energies of the MADN system for different values of \ahfx vs the PBE0 ($\ahfx=0.25$) reference. (f) Site energy disorder $\sigma$ in \unit[]{eV} for all values of \ahfx.}
  \label{fig:Edip_qmmm_MADN}
\end{figure*}

>>>>

\begin{figure*}[tbp]
  \centering
  \includegraphics[width=\linewidth]{fig1.pdf}
  \caption{Schematic representation of the multiscale framework for simulation of charge transport: (a) a representative large-scale morphology is obtained from Molecular Dynamics. (b) Information about the molecular building blocks and the morphology are used to determine the molecular transport graph $\mathbf{G}$ for a given choice of the \ahfx via calculation of reorganization energy, site energies, and electronic couplings. (c) The time-of-flight charge mobility is simulated based on the graph.}
  \label{fig:MSM}
\end{figure*}

@@

\begin{figure}[tbp]
    \centering
    \includegraphics[width=\linewidth]{fig2.pdf}
    \caption{Dependence of molecular parameters as used directly in the multiscale model or in its paramaterization phase on the amount of Hartree--Fock type exchange in the PBE0-based hybrid functional $\alpha_\text{HFX}$. (a) The adiabatic ionization potential, (b) reorganization energy, (c) dipole moment of the neutral molecule, and (d) isotropic molecular polarizability in neutral and charged states, respectively.}
    \label{fig:autogen_MADN}
\end{figure}

@@

\begin{figure*}[tbp]
  \centering
  \includegraphics[width=\linewidth]{fig3.pdf}
  \caption{Panels (a)-(e): Scatter plot of site energies of the MADN system for different values of \ahfx vs the PBE0 ($\ahfx=0.25$) reference. (f) Site energy disorder $\sigma$ in \unit[]{eV} for all values of \ahfx.}
  \label{fig:E_qmmm_MADN}
\end{figure*}

@@

\begin{figure*}[tbp]
  \centering
  \includegraphics[width=\linewidth]{fig4.pdf}
  \caption{Scatter plot of electronic coupling elements of the MADN system for different values of \ahfx vs the PBE0 ($\ahfx=0.25$) reference.}
  \label{fig:J_MADN}
\end{figure*}

@@

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\linewidth]{fig5.pdf}
  \caption{The maximum size of the subgraphs obtained in the percolation algorithm as a function of critical value $J_c$.}
  \label{fig:J_percolate}
\end{figure}

@@

\begin{figure}[tbp]
  \centering
  \includegraphics[width=0.45\textwidth]{fig6.pdf}
  \caption{Distribution of ToFs in the MADN system from  Monte Carlo sampling with a sample size $N_\text{MC}=50000$. The red vertical lines indicate the lower bound and upper bound of the 99\% confidence interval around the median. The black circles indicate the ToF obtained using explicit \ahfx values. Uncertainties considered are (a) in the eorganziation energy, (b) in the site energy, (c) in the coupling elements, and (d) in all simultaneously.}
  \label{fig:mle_MADN_withE}
\end{figure}

@@

\begin{figure}[tbp]
    \centering
    \includegraphics[width=\linewidth]{fig7.pdf}
    \caption{Distribution of the mobility $\mu$ for different values of the externally applied electric field $F$ as obtained from uncertainty quantification using 
    Monte Carlo sampling with a sample size $N_\text{MC}=10000$. The red vertical lines indicate the lower bound and upper bound of the 99\% confidence interval around the median. (a) $|\vec{F}|=4 \cdot 10^7 \unit{V/m}$, (b) $|\vec{F}|=5 \cdot 10^7 \unit{V/m}$, (c) $|\vec{F}|=6 \cdot 10^7 \unit{V/m}$, (d) $|\vec{F}|=7 \cdot 10^7 \unit{V/m}$, (e) $|\vec{F}|=8 \cdot 10^7 \unit{V/m}$, (f) $|\vec{F}|=9 \cdot 10^7 \unit{V/m}$.}
    \label{fig:fig_mle_withE_mu2_ave}
\end{figure}

@@

\begin{figure}[tbp]
    \centering
    \includegraphics[width=0.45\textwidth]{fig8.pdf}
    \caption{Electric-field dependence of the mobility $\mu$ in the multiscale modeled MADN system. The dash lines are Poole--Frenkel plots obtained with specific \ahfx values, and the green shaded area indicates the 99\% confidence interval estimated from the MC sampling with a sample size of $N_\text{MC}=10000$.}
    \label{fig:PF_plot_ave}
\end{figure}

@@

\section{Discussion \& Conclusion}
One key observation of this study of Uncertainty Quantification in multiscale models for charge transport in organic semiconductors due to the choice of exchange-correlation functionals in density functional theory by systematically varying the Hartree--Fock exchange fraction in hybrid functionals is the dominance of site energy uncertainties in influencing the variability of the time-of-flight and mobility predictions. In contrast, the uncertainties in reorganization energies and electronic coupling elements are shown to have a relatively minor effect. This suggests that further efforts to enhance the accuracy of site energy calculations -- potentially through improved parameterization or advanced quantum mechanical methods -- could significantly improve the reliability of multiscale modeling predictions.   Interestingly, the results also demonstrate that the uncertainties in electronic coupling elements, particularly those with very small magnitudes, are less relevant for overall charge transport. This aligns with the percolation analysis, which indicates that coupling elements below a critical threshold contribute minimally to the connectivity of the charge transport network. Thus, simplifying approximations in handling these low-value couplings could be justified in specific scenarios to reduce computational complexity without compromising accuracy.

@@

\bibliography{../references.bib}

\appendix*
\section{Electrostatic and polarized energy contributions}
\begin{figure*}
  \centering
  \includegraphics[width=0.80\textwidth]{fig9.pdf}
  \caption{Panels (a)-(e): Scatter plot of the electrostatic contribution to site energies of the MADN system for different values of \ahfx vs the PBE0 ($\ahfx=0.25$) reference. (f) Site energy disorder $\sigma$ in \unit[]{eV} for all values of \ahfx.}
  \label{fig:Estat_qmmm_MADN}
\end{figure*}

\begin{figure*}
  \centering
  \includegraphics[width=0.80\textwidth]{fig10.pdf}
  \caption{Panels (a)-(e): Scatter plot of polarization contribution to site energies of the MADN system for different values of \ahfx vs the PBE0 ($\ahfx=0.25$) reference. (f) Site energy disorder $\sigma$ in \unit[]{eV} for all values of \ahfx.}
  \label{fig:Edip_qmmm_MADN}
\end{figure*}
